Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-07 Dissertation/Thesis/tex/ae2D.tex
updated from tlee edits, more figs for NRL flight experiment

\paragraph{Expanding Ring}
The expanding ring technique is advantageous for searching local solutions quickly, only considering distant future poses when necessary. The key idea is that future candidate locations lie on a circular ``ring'' centered around the robot, evenly spaced around the ring (see red circles in Figure \ref{fig:OptProcess}), and the ring is expanded if certain criteria are not met. More explicitly, consider $n_c$ candidate locations denoted by $x_c\in\braces{x_1,x_2,\ldots,x_{n_c}}$ located with the distance $\delta$ away from the robot. All candidates must satisfy the inequality constraint,
\begin{align}
\label{eqn:CollisionInequalityConstraint}
P_\text{collision}(X)=1-\prod_{i\in\mathcal C_X}(P(\bar{\mathbf{m}}_i)\leq\beta,
\end{align}
where $\mathcal C_X$ is the set of grid cells falling inside a volume of preselected size around $X$ that may cause collision and $\beta>0$ is a small acceptable probability of collision. Any location that violates an inequality constraint \refeqn{CollisionInequalityConstraint} is excluded to avoid collisions. The set of optimal attitudes at each candidate location is $\braces{R^*_{1},R^*_{2},\ldots,R^*_{n_c}}$, obtained from \refeqn{FindRc}. The information gain objective function for a scan $Z_c$ captured from pose $X_c$ is
\begin{align}
\label{eqn:ObjFun}
\mathcal I(X_c)=H(P(m))-\text{E}\left[H(P(m|X_c,Z_c))\right],
\end{align}
is computed by a summation about the $n_d$ rays as %\refeqn{Objective},
\begin{align}
\label{eqn:ObjFunApprox}
\mathcal I(x_c,R_c^*)&\approx \sum_{z_{c,i}\in R_{c}^*\text{ FOV}}\bigg(H(P(m))-\text{E}\left[H(P(m|x_c,z_{c,i}))\right]\bigg),
\\
x_c^*&=\argmax_{x_c}\mathcal I(x_c,R_c^*).
\end{align}
At the optimal pose $X^*_c=(x^*_c,R^*_c)$, the resulting information gain must satisfy $\mathcal I(X_c^*)\geq\mathcal I_\text{min}$, where $\mathcal I_\text{min}$ is a minimum threshold for expected information gain; robot motion is only justified when the expected information gain is significantly large. If the minimum threshold is not met, the ring of candidate pose locations is increased such that $n_c$ and $\delta$ are multiplied by a scale function $\lambda>1$.
This process is repeated until the expected information gain of the optimal pose is at least $\mathcal I_\text{min}$, or all candidates lie in collision zones or outside map limits. %A pseudocode of the process is found in Table \ref{tab:Alg_AutomousExploration}.

@@

Knowing only that the robot is inside free space at the beginning, the robot carefully navigates the environment while avoiding collisions. The robot motion is governed by a policy that maximizes the map information gain within its set of pose candidates, where the $\hat n=6$ is chosen to approximate the expected entropy of each ray. 
When running the exploration algorithm within the framework of the Robot Operating System (ROS), the mean computation time is $0.0194$ seconds to determine the optimal future pose and complete Dijkstra's algorithm on the occupancy grid.
The computation times for this map reached roughly $1$ second at maximum, corresponding to rare cases when the robot is locally surrounded by a highly-certain environment; this task requires evaluating many more pose candidates and motion planning over a larger terrain.

>>>>

\paragraph{Expanding Ring}
The expanding ring technique is advantageous for searching local solutions quickly, only considering distant future poses when necessary. The key idea is that future candidate locations lie on a circular ``ring'' centered around the robot, evenly spaced around the ring (see red circles in Figure \ref{fig:OptProcess}), and the ring is expanded if certain criteria are not met. More explicitly, consider $n_c$ candidate locations denoted by $x_c\in\braces{x_1,x_2,\ldots,x_{n_c}}$ located with the distance $\delta$ away from the robot. All candidates must satisfy the inequality constraint,
\begin{align}
\label{eqn:CollisionInequalityConstraint}
P_\text{collision}(X)=1-\prod_{i\in\mathcal C_X}(P(\bar{\mathbf{m}}_i)\leq\beta,
\end{align}
where $\mathcal C_X$ is the set of grid cells falling inside a volume of preselected size around $X$ that may cause collision and $\beta>0$ is a small acceptable probability of collision. Any location that violates an inequality constraint \refeqn{CollisionInequalityConstraint} is excluded to avoid collisions. The set of optimal attitudes at each candidate location is $\braces{R^*_{1},R^*_{2},\ldots,R^*_{n_c}}$, obtained from \refeqn{FindRc}. The information gain objective function for a scan $Z_c$ captured from pose $X_c$ is
\begin{align}
\label{eqn:ObjFun}
\mathcal I(X_c)=H(P(m))-\text{E}\left[H(P(m|X_c,Z_c))\right],
\end{align}
is computed by a summation about the $n_d$ rays as %\refeqn{Objective},
\begin{align}
\label{eqn:ObjFunApprox}
\mathcal I(x_c,R_c^*)&\approx \sum_{z_{c,i}\in R_{c}^*\text{ FOV}}\bigg(H(P(m))-\text{E}\left[H(P(m|x_c,z_{c,i}))\right]\bigg),
\\
x_c^*&=\argmax_{x_c}\mathcal I(x_c,R_c^*).
\end{align}
At the optimal pose $X^*_c=(x^*_c,R^*_c)$, the resulting information gain must satisfy $\mathcal I(X_c^*)\geq\mathcal I_\text{min}$, where $\mathcal I_\text{min}$ is a minimum threshold for expected information gain; robot motion is only justified when the expected information gain is significantly large. If the minimum threshold is not met, the ring of candidate pose locations is increased such that $n_c$ and $\delta$ are multiplied by a scale function $\lambda>1$.
This process is repeated until the expected information gain of the optimal pose is at least $\mathcal I_\text{min}$, or all candidates lie in collision zones or outside map limits. %A pseudo-code of the process is found in Table \ref{tab:Alg_AutomousExploration}.

@@

Knowing only that the robot is inside free space at the beginning, the robot carefully navigates the environment while avoiding collisions. The robot motion is governed by a policy that maximizes the map information gain within its set of pose candidates, where the $\hat n=6$ is chosen to approximate the expected entropy of each ray. 
When running the exploration algorithm within the framework of the Robot Operating System (ROS)~\cite{ROS}, the mean computation time is $0.0194$ seconds to determine the optimal future pose and complete Dijkstra's algorithm on the occupancy grid.
The computation times for this map reached roughly $1$ second at maximum, corresponding to rare cases when the robot is locally surrounded by a highly-certain environment; this task requires evaluating many more pose candidates and motion planning over a larger terrain.

### 2018-07-07 Dissertation/Thesis/tex/conclusions.tex
updated from tlee edits, more figs for NRL flight experiment

This concludes the dissertation. We propose several contributions in probabilistic occupancy grid mapping and autonomous exploration in 2D and 3D environments in single- and multi-vehicle scenarios. Computational efficiency and numerical accuracy are held paramount in derivations and algorithmic structure. Several numerical examples and experiments demonstrate the efficacy of each contribution.

@@

>>>>

\section{Summary of Contributions}
In this dissertation, we propose several contributions in probabilistic occupancy grid mapping and autonomous exploration in 2D and 3D environments in single- and multi-vehicle scenarios. Computational efficiency and numerical accuracy are held paramount in derivations and algorithmic structure. Several numerical examples and experiments demonstrate the efficacy of each contribution.

@@

\section{Future Directions}

### 2018-07-07 Dissertation/Thesis/tex/frontmatter.tex
updated from tlee edits, more figs for NRL flight experiment

\showcommitteepage % hide this page if you're doing a MS thesis
%\hidecommitteepage 
\committee{ %
Taeyoung Lee\\
Department of Mechanical and Aerospace Engineering\\
The George Washington University\\ 
Dissertation Director\\ % remember to add a space between committee members

@@

James Hahn\\
Department of Computer Science\\
The George Washington University\\
Committee Member\\

>>>>

\showcommitteepage % hide this page if you're doing a MS thesis
%\hidecommitteepage 
\committee{ %

James Hahn\\
Department of Computer Science\\
The George Washington University\\
Committee Chair\\

Taeyoung Lee\\
Department of Mechanical and Aerospace Engineering\\
The George Washington University\\ 
Committee Member\\ % remember to add a space between committee members

@@

### 2018-07-07 Dissertation/Thesis/tex/intro.tex
updated from tlee edits, more figs for NRL flight experiment

% JINT17: This paper proposes a computationally efficient algo- rithm to construct the exact inverse sensor model. More explicitly, for a given forward sensor model defined by the probability distribution of range measurements, this algo- rithm yields the a posteriori probabilities of occupancy of all the cells within the area covered by the range sensor from the range measurements. The key idea is reducing the computational load by using the fact that if a cell is occu- pied, the occupancies of the other cells blocked by it is irrelevant to the forward sensor model, and this property is systematically utilized with various probabilistic prop- erties to derive a computationally-efficient solution to the inverse sensor model. Furthermore, the proposed approach integrates a priori probabilities of occupancy and multiple range measurements according to the Bayesian framework to obtain more accurate maps. As such, it contrasts from the existing framework based on log-odds ratios that impose an additional Markov assumption.

@@

% TODO: update this list
% TL: the paper in preparation can be added as well

\begin{itemize}
	\item E. Kaufman, K. Takami, Z. Ai, and T. Lee, ``Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities,'' \textit{The Second IEEE International Conference on Robotic Computing}, Laguna Hills, January 2018, pp. 49--55.
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Autonomous Exploration with Exact Inverse Sensor Models,'' \textit{Journal of Intelligent }\&\textit{ Robotic Systems}, 2017, doi: 10.1007/s10846-017-0710-7.
	\item E. Kaufman, T. Lee, and Z. Ai, ``Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping,'' \textit{IEEE International Conference on Simulation, Modeling, and Programming for Autonomous Robots}, San Francisco, December 2016, pp. 246--251.
	\item E. Kaufman, T. Lee, Z. Ai, and I. S. Moskowitz, ``Bayesian Occupancy Grid Mapping via an Exact Inverse Sensor Model,'' \textit{Proceedings of the American Control Conference}, Boston, July 2016, pp. 5709-5715.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{The Journal of the Astronautical Sciences}, 63(1): pp. 60-80, 2016, doi: 10.1007/s40295-015-0082-9.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking,'' \textit{The Journal of the Astronautical Sciences}, 63(4): pp. 308-334, 2016, doi: 10.1007/s40295-016-0092-2.
	\item T. Wu, E. Kaufman, and T. Lee, ``Globally Asymptotically Stable Attitude Observer on SO(3),'' \textit{Proceedings of the 54th IEEE Conference on Decision and Control}, pp. 2164-2168, Osaka, Japan, December 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting}, Williamsburg, VA, Jan. 2015, AAS 15-451.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filter and Coalescence Avoidance Performance Evaluations,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting, Williamsburg}, VA, Jan. 2015, AAS 15-432.
	\item E. Kaufman, K. Caldwell, D. Lee, and T. Lee, ``Design and Development of a Free-Floating Hexrotor UAV for 6-DOF Maneuvers,'' \textit{Proceedings of the IEEE Aerospace Conference}, Mar. 2014, ASC 14-2527.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Optimal Joint Probabilistic Data Association Filter Avoiding Coalescence in Close Proximity,'' \textit{Proceedings of the European Control Conference}, pp. 2709-2714, June 2014.
	\vspace*{0.5cm}
\end{itemize}

>>>>

@@

\begin{itemize}
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Multi-Vehicle Cooperative Exploration and Patrol of Uncertain 3D Environments'', in preparation.
	\item E. Kaufman and T. Lee, ``Autonomous Aerial Exploration for Topological Mapping of Mars Environments'', \textit{2019 AIAA Guidance, Navigation, and Control Conference}, San Diego, CA, USA, January 2019, submitted.
	\item E. Kaufman, K. Takami, Z. Ai, and T. Lee, ``Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities,'' \textit{The Second IEEE International Conference on Robotic Computing}, pp. 49--55, Laguna Hills, January 2018.
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Autonomous Exploration with Exact Inverse Sensor Models,'' \textit{Journal of Intelligent }\&\textit{ Robotic Systems}, 2017, doi: 10.1007/s10846-017-0710-7.
	\item E. Kaufman, T. Lee, and Z. Ai, ``Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping,'' \textit{IEEE International Conference on Simulation, Modeling, and Programming for Autonomous Robots}, pp. 246--251, San Francisco, CA, USA, December 2016.
	\item E. Kaufman, T. Lee, Z. Ai, and I. S. Moskowitz, ``Bayesian Occupancy Grid Mapping via an Exact Inverse Sensor Model,'' \textit{Proceedings of the American Control Conference}, pp. 5709-5715, Boston, MA, USA, July 2016.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{The Journal of the Astronautical Sciences}, 63(1): pp. 60-80, 2016, doi: 10.1007/s40295-015-0082-9.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking,'' \textit{The Journal of the Astronautical Sciences}, 63(4): pp. 308-334, 2016, doi: 10.1007/s40295-016-0092-2.
	\item T. Wu, E. Kaufman, and T. Lee, ``Globally Asymptotically Stable Attitude Observer on SO(3),'' \textit{Proceedings of the 54th IEEE Conference on Decision and Control}, pp. 2164-2168, Osaka, Japan, December 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting}, AAS 15-451, Williamsburg, VA, January 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filter and Coalescence Avoidance Performance Evaluations,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting, Williamsburg}, AAS 15-432, VA, January 2015.
	\item E. Kaufman, K. Caldwell, D. Lee, and T. Lee, ``Design and Development of a Free-Floating Hexrotor UAV for 6-DOF Maneuvers,'' \textit{Proceedings of the IEEE Aerospace Conference}, ASC 14-2527, March 2014, Big Sky, MT, USA.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Optimal Joint Probabilistic Data Association Filter Avoiding Coalescence in Close Proximity,'' \textit{Proceedings of the European Control Conference}, pp. 2709-2714, Strasbourg, France, June 2014.
	\vspace*{0.5cm}
\end{itemize}

### 2018-07-07 Dissertation/Thesis/tex/pogm.tex
updated from tlee edits, more figs for NRL flight experiment

In this chapter, we present the exact solution to occupancy probability for a given depth measurement. This Bayesian approach uses the stochastic properties of sensors, and exploits important patterns in conditional probabilities. This solution is simulated in several examples to show the efficacy of the approach.

@@

The synergistic scan inverse sensor model algorithm is summarized with the pseudocode of Algorithm \ref{alg:SynergisticScanISM} as a computationally efficient, recursive algorithm that avoids repeated calculations of the same quantity. This algorithm utilizes the following temporary variables to develop the algorithm in an efficient recursive form, defined as
\begin{align*}
a_k&=\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,i},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1}),
\\
b_k&=\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1}),
\nonumber\\
c_k&=\frac{
\sum_{i=k+1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})}{P(\bar{\mathbf{r}}_{l,k}|X_{1:t-1},Z_{1:t-1})},
\end{align*}
as well as $d$ and $e$ for the two terms composing \refeqn{xi}. Once again, the history of poses and measurement scans are removed from the pseudo-code for simplicity.

>>>>

In this chapter, we present the exact solution to occupancy grid map probability for a given depth measurement. This Bayesian approach uses the stochastic properties of sensors, and exploits important patterns in conditional probabilities. Then we show how several measurements can be considered together in 2D. This solution is simulated with numerical examples to show the efficacy of the approach.

@@

The synergistic scan inverse sensor model algorithm is summarized with the pseudo-code of Algorithm \ref{alg:SynergisticScanISM} as a computationally efficient, recursive algorithm that avoids repeated calculations of the same quantity. This algorithm utilizes the following temporary variables to develop the algorithm in an efficient recursive form, defined as
\begin{align*}
a_k&=\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,i},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1}),
\\
b_k&=\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1}),
\nonumber\\
c_k&=\frac{
\sum_{i=k+1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})}{P(\bar{\mathbf{r}}_{l,k}|X_{1:t-1},Z_{1:t-1})},
\end{align*}
as well as $d$ and $e$ for the two terms composing \refeqn{xi}. Once again, the history of poses and measurement scans are removed from the pseudo-code for simplicity.
